Type Refinements for the Working Class

### 2015-11-12 paper.tex
Clean up previous work

\newcommand\HypJ[2]{#1\ \ (#2)}
\newcommand\GenJ[2]{\vert_{\IMode{#1}}\; #2}

@@

\newcommand\MV[1]{\mathfrak{#1}}
\newcommand\MApp[3]{#1\{#2\}(#3)}
\newcommand\App[2]{#1(#2)}
\newcommand\Dom[1]{\left\vert#1\right\vert}
\newcommand\FV[1]{\mathbf{FV}\left(#1\right)}
\newcommand\FS[1]{\mathbf{FS}\left(#1\right)}
\newcommand\NotIn[2]{\IMode{#1}\notin\IMode{#2}}
\newcommand\SortExp{\mathsf{exp}}

@@

\begin{definition}[General Judgment]
  For a metavariable context $\IsMetaCtx{\Omega}$, we can define the presheaf
  of its substitutions $\Of{\square\Omega}{\Sets^\SCtx}$ as follows:
  \[
    \Define{{\square\Omega}\,(\Upsilon)}{
      \prod_{(\MV{m}:v)\in\Omega}
        \MkSet{E\mid\IsAbtUnmoded{\cdot}{\Upsilon}{\cdot}{E}{v}}
    }
  \]

  For any diagram $\Of{\mathcal{J}}{\mathbb{J}^{\square\Omega(\Upsilon)}}$, we can define
  the general judgment $\GenJ{\Omega}{\mathcal{J}}$ as follows, where
  $\Of{\Yoneda{-}}{\mathcal{W}\to\mathbb{J}}$ is the Yoneda Embedding:
   \[
     \textstyle
     \Define{
       \left(\GenJ{\Omega}{\mathcal{J}}\right)(w)
     }{
       \Hom{\mathbb{J}}{
         \Yoneda{w}
       }{
         Lan_{\mathbbold{1}}{\mathcal{J}}
       }
     }
   \]

   Intuitively, the general judgment $\GenJ{\Omega}{\mathcal{J}}$ is evident
   when the family of judgments $\mathcal{J}$ shall forevermore have a section
   (i.e. for any substitution $\Member{\omega}{\square\Omega(\Upsilon)}$,
   $\mathcal{J}(\omega)$ shall be evident). Recall that metavariables have
   \emph{valences} rather than sorts; as such, the general judgment allows us to
   quantify over terms of higher type.  However, for clarity we will often write
   $\GenJ{\MV{m}:\sigma}{\mathcal{J}}$ rather than
   $\GenJ{\MV{m}:\MkValence{\cdot}{\cdot}{\sigma}}{\mathcal{J}}$; likewise, in
   the body of $\mathcal{J}$ we will simply write $\MV{m}$ rather than the more
   proper $\MApp{\MV{m}}{\cdot}{\cdot}$.

@@

\paragraph{Case} $\DefPRefinesCtxSnoc{\Phi}{\Psi}{x}{\chi}{\Gamma}{\sigma}$.
\begin{gather*}
  \infer{
    \HEqRefines{\Phi}{\Psi,x:\chi}{\phi}{\psi}{\tau}
  }{
    \GenJ{y,z:\sigma}{
      \HypJ{
        \HEqRefines{\Phi}{\Psi}{\Subst{y}{x}{\phi}}{\Subst{z}{x}{\psi}}{\tau}
      }{
        \HRMemEq{\Phi}{\Psi}{y}{z}{\chi}
      }
    }
  }
\end{gather*}

>>>>

\newcommand\HypJ[2]{#1\ \ (#2)}
\newcommand\GenJ[2]{\vert_{\IMode{#1}}\; #2}
\newcommand\HPGenJ[4]{\vert^{\IMode{#1}\parallel\IMode{#2}}_{\IMode{#3}}\; #4}

@@

\newcommand\MV[1]{\mathfrak{#1}}
\newcommand\MApp[3]{%
  #1
  \ifthenelse{\equal{#2}{}}{}{%
    \{#2\}%
  }%
  \ifthenelse{\equal{#3}{}}{}{%
    [#3]%
  }
}
\newcommand\App[2]{#1(#2)}
\newcommand\Dom[1]{\left\vert#1\right\vert}
\newcommand\FV[1]{\mathbf{FV}\left(#1\right)}
\newcommand\FS[1]{\mathbf{FS}\left(#1\right)}
\newcommand\NotIn[2]{\IMode{#1}\notin\IMode{#2}}
\newcommand\SortExp{\mathsf{exp}}

@@

\begin{definition}[General Judgment]
  For a metavariable context $\IsMetaCtx{\Omega}$, we can define the set
  of its substitutions as follows:
  \[
    \Define{{\square\Omega}}{
      \prod_{(\MV{m}:v)\in\Omega}
        \MkSet{E\mid\IsAbtUnmoded{\cdot}{\Upsilon}{\cdot}{E}{v}}
    }
  \]

  For any diagram $\Of{\mathcal{J}}{\mathbb{J}^{\square\Omega}}$, we can define
  the general judgment $\GenJ{\Omega}{\mathcal{J}}$ as follows, where
  $\Of{\Yoneda{-}}{\mathcal{W}\to\mathbb{J}}$ is the Yoneda Embedding:
   \[
     \textstyle
     \Define{
       \left(\GenJ{\Omega}{\mathcal{J}}\right)(w)
     }{
       \Hom{\mathbb{J}}{
         \Yoneda{w}
       }{
         Lan_{\mathbbold{1}}{\mathcal{J}}
       }
     }
   \]

   Intuitively, the general judgment $\GenJ{\Omega}{\mathcal{J}}$ is evident
   when the family of judgments $\mathcal{J}$ shall forevermore have a section
   (i.e. for any substitution $\Member{\omega}{\square\Omega}$,
   $\mathcal{J}(\omega)$ shall be evident). Recall that metavariables have
   \emph{valences} rather than sorts; as such, the general judgment allows us to
   quantify over terms of higher type.

   \paragraph{Notation}

   We will write $\HPGenJ{\Upsilon}{\Gamma}{\Omega}{\mathcal{J}}$ for
   $\GenJ{\Omega'}{\mathcal{J}}$, where
   $\Lookup{\Omega'}{\MV{m}}{\MkValence{\Upsilon,\vec{\sigma}}{\Gamma,\vec{\tau}}{\tau}}$
   if $\Lookup{\Omega}{\MV{m}}{\MkValence{\vec{\sigma}}{\vec{\tau}}{\tau}}$.
   Additionally, for clarity we will often write
   $\GenJ{\MV{m}:\sigma}{\mathcal{J}}$ rather than
   $\GenJ{\MV{m}:\MkValence{\cdot}{\cdot}{\sigma}}{\mathcal{J}}$; likewise, in
   the body of $\mathcal{J}$, when there is a contextually salient
   $\vec{u}$, we will simply write $\MV{m}$ rather than the more proper
   $\MApp{\MV{m}}{\vec{u}}{\cdot}$.

@@

\paragraph{Case} $\DefPRefinesCtxSnoc{\Phi}{\Psi}{x}{\chi}{\Gamma}{\sigma}$,
where $\RefinesCtx{\Phi}{\Upsilon}$.

\begin{gather*}
  \infer{
    \HEqRefines{\Phi}{\Psi,x:\chi}{\phi}{\psi}{\tau}
  }{
    \HPGenJ{\Upsilon}{\Gamma}{y,z:\sigma}{
      \HypJ{
        \HEqRefines{\Phi}{\Psi}{
          \Subst{y}{x}{\phi}
        }{
          \Subst{z}{x}{\psi}
        }{\tau}
      }{
        \HRMemEq{\Phi}{\Psi}{y}{z}{\chi}
      }
    }
  }
\end{gather*}
